¿Qué pueden hacer las escuelas para disminuir la desigualdad en el conocimiento cívico?

### 2020-07-31 processing/analysis.Rmd
guardar imagenes

# Análisis descriptivo
```{r}
summary(data)
```

```{r}
hist(data$PV1CIV)
```

# Análisis bivariado 
```{r}
basecor<-select(data,m_nse, nse, m_cult_part, m_apert_disc, m_esp_part,m_nse, PV1CIV)

>>>>

# AnC!lisis descriptivo
```{r}
summary(data)
```

```{r}
png("../output/graphs/histograma.png",
    width = 15,height = 15,units="cm",
    pointsize=12,bg="white",res=300)

hist(data$PV1CIV)

dev.off()

# AnC!lisis bivariado 
```{r}
basecor<-select(data,m_nse, nse, m_cult_part, m_apert_disc, m_esp_part,m_nse, PV1CIV)
